\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-11-27 paper/m-lb-m-technometrics.tex
Change TeX as needed for Technometrics

% Template for the submission to:
%   The Annals of Probability           [aop]
%   The Annals of Applied Probability   [aap]
%   The Annals of Statistics            [aos] 
%   The Annals of Applied Statistics    [aoas]
%   Stochastic Systems                  [ssy]
%
%Author: In this template, the places where you need to add information
%        (or delete line) are indicated by {???}.  Mostly the information
%        required is obvious, but some explanations are given in lines starting
%Author:
%All other lines should be ignored.  After editing, there should be
%no instances of ??? after this line.

% use option [preprint] to remove info line at bottom
% journal options: aop,aap,aos,aoas,ssy
% natbib option: authoryear
\documentclass[aoas]{imsart}
\RequirePackage{natbib}
\usepackage{amsthm,amsmath,natbib,enumerate}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url, imsart}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\bibliographystyle{imsart-nameyear}
%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

% provide arXiv number if available:
%\arxiv{arXiv:0000.0000}

@@

\newcommand{\ind}{\stackrel{ind.}{\sim}}
\newcommand{\op}{\operatorname}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\myequation}{\begin{equation}}
\newcommand{\myendequation}{\end{equation}}
\let\[\myequation
\let\]\myendequation
% put your definitions there:
\startlocaldefs
\endlocaldefs

@@

\begin{frontmatter}

% "Title of the paper"
\title{A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes}

\begin{aug}
  \author{\fnms{Eric}  \snm{Mittman}\corref{}\ead[label=e1]{first@somewhere.com}},
  \author{\fnms{Colin} \snm{Lewis-Beck}\ead[label=e2]{second@somewhere.com}}
  \and
  \author{\fnms{William Q.}  \snm{Meeker}%
  \ead[label=e3]{third@somewhere.com}%
  \ead[label=u1,url]{http://www.foo.com}}

  %\thankstext{t2}{Footnote to the first author with the `thankstext' command.}

  %\runauthor{F. Author et al.}

  \affiliation{Iowa State University}

  %\address{Address of the First and Second authors,\\ 
   %       \printead{e1,e2}}

  %\address{Address of the Third author,\\
   %       \printead{e3,u1}}

\end{aug}

% indicate corresponding author with \corref{}
% \author{\fnms{John} \snm{Smith}\corref{}\ead[label=e1]{smith@foo.com}\thanksref{t1}}
% \thankstext{t1}{Thanks to somebody} 
% \address{line 1\\ line 2\\ printead{e1}}
%\author{\fnms{Eric Mittman and Colin Lewis-Beck and William Q. Meeker}}
%\affiliation{Iowa State University}
%\address{\printead{e1}}
%\and
%\author{\fnms{???} \snm{???}\ead[label=e2]{???}}
%\address{\printead{e2}}
%\affiliation{???}

%\runauthor{???}

@@

\begin{keyword}
\kwd{GLFP, Bathtub hazard, Censored data, Hierarchical models, Bayesian estimation}
%\kwd{}
\end{keyword}

\end{frontmatter}

@@

\begin{supplement}
\sname{Supplement A}
\stitle{Model code and plots}
\slink[url]{http://www.e-publications.org/ims/support/dowload/imsart-ims.zip}
\sdescription{Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6.}
\end{supplement}
\begin{supplement}
\sname{Supplement B}
\stitle{Backblaze data set}
\slink[url]{http://www.e-publications.org/ims/support/dowload/imsart-ims.zip}
\sdescription{Lifetime data set for all 44 drive-models used in our analysis.}
\end{supplement}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\newcommand{\ind}{\stackrel{ind.}{\sim}}
\newcommand{\op}{\operatorname}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\myequation}{\begin{equation}}
\newcommand{\myendequation}{\end{equation}}
\let\[\myequation
\let\]\myendequation

\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

@@

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes}
  \author{Eric Mittman\thanks{Department of Statistics, Iowa State University}\\
    and \\
    Colin Lewis-Beck\footnotemark[1]\\
    and \\
    William Q. Meeker\footnotemark[1]}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Title}
\end{center}
  \medskip
} \fi

@@

\noindent%
{\it Keywords:} GLFP, Bathtub hazard, Censored data, Hierarchical models, Bayesian estimation
\vfill

\newpage
% \tableofcontents
% \newpage
\spacingset{1.45} % DON'T change the spacing!

@@

\section{Supplementary Material}
\label{sec:supple}

\begin{description}

\item[Model code and plots] Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6 (supplementary.pdf)

\item[Backblaze data set] Lifetime data set for all 44 drive-models used in our analysis. (backblaze\_hd\_data.csv)

\end{description}
